### 2011-10-20 AffineLieAlgebras/Thesis/1.tex
Added (almost) all texts and figures to thesis. Some work on SLE paper.

\section{Теория представлений аффинных алгебр Ли}
\label{sec:representation-theory}
Определение аффинных алгебр. Корни, веса, кратности. Категория О.

@@

>>>>

\section{Теория представлений аффинных алгебр Ли}
\label{sec:representation-theory}

\subsection{Алгебра петель и центральное расширение}
\label{sec:loop-algebra-central-extension}

Определение аффинных алгебр. Корни, веса, кратности. Категория О.

\subsection{Представления аффинных алгебр Ли}
\label{sec:affine-lie-algebra-representations}

@@

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of an arbitrary
  reductive subalgebra. In particular we consider the situation where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan and the analogue of the Weyl numerator -- the tools that describe
  explicitly the recurrent properties of branching coefficients.
  Possible applications of fan technique in CFT models are considered.
\end{abstract}

\subsection{Introduction}
\label{sec:introduction}

The branching problem for affine Lie algebras emerges in conformal field theory, for example,
in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
Recently the problem of conformal embeddings was considered in \cite{coquereaux2008conformal}.

There are different approaches to deal with branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or some
combinatorial methods applied in \cite{feigin707principal}.

In this paper we prove that
for an arbitrary reductive subalgebra branching coefficients are subject to
a set of recurrent properties that can be explicitly formulated and that there exists
an effective and simple algorithm to solve these recurrent relations step by step.
The basic idea is similar to the one used in \cite{ilyin812pbc} for maximal embeddings.
In our case the algorithm is essentially different, new properties of singular weights
are determined to deal with an arbitrary reductive injection $\frak{a} \rightarrow \frak{g}$.

The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ orthogonal to $\af$.
For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
$\left(  \af, \afb \right)$ the element
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct a recurrent property for branching coefficients corresponding
to the injection $\frak{a} \rightarrow \frak{g} $.
The property is formulated in
terms of the specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
subalgebras of finite-dimensional or affine Lie algebras.
In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
becomes trivial
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
and the relations described earlier in \cite{ilyin812pbc} are reobtained.

We demonstrate that our algorithm is effective and can be used in studies
of conformal embeddings and coset constructions in rational conformal field theory.

The paper is organized as follows. In the subsection \ref{sec:notation}  we fix the general notations.
In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. Affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
General properties of the proposed algorithm and
possible further developments are also discussed (Section \ref{sec:conclusion}).

\subsubsection{Notation}
\label{sec:notation}

Consider affine Lie algebras $\frak{g}$ and $\af$ with
underlying finite-dimensional subalgebras $\go$ and $%
\ao$ and an injection $\af\longrightarrow \frak{g%
}$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\af}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
}_{\go}^{\ast }$\
.
We use the following notations:

$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$
-module with the highest weight $\nu $ );

$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\frak{g}$ $%
\left( \mbox{resp. }\af\right) $ ;

$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
root system (of $\frak{g}$ and $\af$ respectively);

$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
$ (resp. in $\left( \Delta _{\af}\right) $);

$\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
\right)$ --- the finite root system of the subalgebra $\co{%
\frak{g}}$ (resp. $\co{\af}$);

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ --- the
weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right)
$ ;

$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;

$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;

$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;

$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;

$\epsilon \left( w\right) :=\det \left( w\right) $ ;

$\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

$\delta $ --- the imaginary root of $\frak{g}$ (and of $\af$ if any);

$\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

$\co{\xi }$ , $\co{\xi _{\left( \af\right) }}$
--- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
resp. }\xi _{\left( \af\right) }\in P_{\af}\right) $;

$\lambda =\left( \co{\lambda };k;n\right) $ ---
decomposition of the affine weight $\lambda$ indicating the finite
part $\co{\lambda }$, the level $k$ and the grade $n$;

$P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
resp. }\in P_{\af}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\af}^{\nu } $);

$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\af}^{\nu
}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
L_{\af}^{\nu }\right) $;

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $
$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
\left( \alpha \right) }}\right) $--- the Weyl denominator.

\subsection{Recurrent relations for branching coefficients.}
\label{sec:recurr-form-branch}

Consider an integrable module $L^{\mu }$
of $\frak{g}$ with the highest weight $\mu $ and
let $\af\subset \frak{g}$ be a reductive subalgebra of $\frak{g}$.
With respect to $\af$ the module $L^{\mu }$ is completely reducible,
\begin{equation*}
 L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
\end{equation*}
Using the projection operator $\pi_{\af}$ (to the weight space $\frak{h_a}^*$)
one can  rewrite this decomposition in terms of formal characters:
\begin{equation}
\label{branching1}
 \pi _{\af}\circ ch\left( L^{\mu }\right)
 =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
\end{equation}
We are interested in branching coefficients $b^{(\mu)}_{\nu}$.

\subsubsection{Orthogonal subalgebra and injection fan.}
\label{subsec:branching-orthog-pair}

In this subsection we shall introduce some simple constructions that will be used
in our studies of branching and in particular the "orthogonal partner" $\afb$ for a
reductive subalgebra $\af$  in  $\gf$.

In the Weyl-Kac formula both numerator and denominator  can be considered
as formal elements containing the singular weights of the Verma modules $V^{\xi}$
with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
We attribute singular elements to the corresponding integrable modules $L^{\mu }$
and $L_{\af}^{\nu }$:
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho },
\end{equation*}
\begin{equation*}
\Psi _{ \af}^{\left( \nu \right) }:=
\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\af}})-\rho _{_{\af}}}.
\end{equation*}
and use the Weyl-Kac formula in the form
\begin{equation}
\label{Weyl-Kac2}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\end{equation}

Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
we get the relation connecting the
singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{ \af}^{\left( \nu \right) }$ :
\begin{eqnarray}
\nonumber
\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}%
\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:4} \\
\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{ \frak{%
a}}^{\left( \nu \right) }}{R_{\af}}.
\end{eqnarray}
Here $\Delta _{\af}^{+}$ is the set of
positive roots of the subalgebra $\af$ (without loss of generality we consider
them as vectors from the positive root space $\frak{h}^{\ast  +}$ of $\frak{g}$).

Consider the root subspace
$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }
|\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\af$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

For the Cartan subalgebra we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
\frak{h}_{\af}.
\end{equation}
For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
\end{equation}
\begin{equation}
\label{defect-perp}
\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
_{\perp }}\circ\rho .
\end{equation}
For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
weights $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$ and
their projections to $h_{\widetilde{\af_{\perp }}}^{\ast }$ (additionally
shifted by the defect $-\mathcal{D}_{\af_{\perp }}$):
\begin{equation*}
\mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
}},\quad w\in W.
\end{equation*}
Among the weights $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)
|w\in W\right\}$ choose those located in the fundamental chamber $\overline{C_{%
\widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
u $ for classes $W/W_{\af_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For the same set $U$ introduce the weights
\begin{equation*}
\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\af_{\perp }}.
\end{equation*}
To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
weights.

To describe the recurrent properties for branching coefficients $b_{\nu
}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
main tools is the set of weights $\Gamma _{\af\rightarrow \frak{g}%
} $ called the injection fan. As far as we consider the general situation
(where the injection is not necessarily maximal) the notion of the injection fan is
modified:

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}
In the next subsection we shall see how the injection fan defines the recurrent
properties of branching coefficients. It must be noticed that the injection fan is
the universal instrument that depends only on the injection.

\subsubsection{Decomposing the singular element.}
\label{subsec:decomp-sing-element}

Now we shall prove that the Weyl-Kac character formula (in terms of singular
elements) describes the particular case of a more general relation:

\begin{lemma}
\label{lemma}
Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
\frak{h}_{\perp }$ ,

$L^{\mu }$ be the highest weight module with the singular element
$\Psi ^{\left(\mu \right)}$ ,

$R_{\af_{\perp }}$ be the Weyl denominator for $\af_{\perp }$.

Then the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}\right) $
can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
singular weights $e^{\mu _{\af}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
\end{equation}
\end{lemma}

\begin{proof}
With $u\in U $   and $v\in W_{\afb}$ apply the decomposition
\begin{equation*}
u(\mu +\rho )=\pi _{\af } u(\mu +\rho )+\pi _{
\widetilde{\af_{\perp }} } u(\mu +\rho )
\end{equation*}
to the singular weight
\begin{equation}
\label{sing-decomp-1}
\begin{array}{lcl}
vu(\mu +\rho )-\rho &=&\pi _{ \af }\left( u(\mu +\rho
)\right) -\rho +\rho _{\af_{\perp }}+\pi _{ \hfb }\rho \\
&& + \ v\left( \pi _{ \widetilde{%
\af_{\perp }} }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{ \hfb }\rho.
\end{array}
\end{equation}
Use the defect $\mathcal{D}_{\afb}$ (\ref{defect-perp}) to simplify
the first summand in (\ref{sing-decomp-1}):
\begin{equation*}
\begin{array}{r}
\pi _{ \af }\left( u(\mu +\rho )\right) -\rho +\rho _{%
\mathfrak{a}_{\perp }}+\pi _{ \hfb }\rho = \\
\pi _{ \af }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
-\pi _{\afb}\rho +\rho _{\afb}= \\
=\pi _{ \af }\left( u(\mu +\rho )-\rho \right) +%
\mathcal{D}_{\afb},
\end{array}
\end{equation*}
and the second one:
\begin{equation*}
\begin{array}{c}
v\left( \pi _{ \widetilde{%
\af_{\perp }} }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{ \hfb }\rho=\\
v\left( \pi _{ \widetilde{%
\afb} }u(\mu +\rho )
- \mathcal{D}_{\afb} - \pi _{ \afb }\rho-\pi _{ \hfb }\rho
+\rho _{\afb}\right) -\rho _{\afb}=\\
=v\left( \pi _{ \widetilde{%
\afb} }\left[ u(\mu +\rho )-\rho\right]
- \mathcal{D}_{\afb}
+\rho _{\afb}\right) -\rho _{\afb}.
\end{array}
\end{equation*}
These expressions provide a kind of a factorization in the anomalous element $\Psi^{\mu
}$ and we find in it the combination of
anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
subalgebra $\widetilde{\af_{\perp }}$-modules $L_{\widetilde{\af%
_{\perp }}}^{\eta }$:
\begin{equation*}
\begin{array}{l}
\Psi^{\mu }=\sum_{u\in U}\sum_{v\in W_{\af_{\perp }}}
\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
(v)e^{v\left( \pi _{ \widetilde{\af_{\perp }} }\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}+\rho _{\af%
_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af }\left[ u(\mu
+\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\Psi _{\widetilde{%
\af_{\perp }}}^{\pi _{ \widetilde{\af_{\perp }} }%
\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}}
\end{array}
\end{equation*}

Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
\in \Delta _{\af_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
desired relation:
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
}}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{
\widetilde{\af_{\perp }} }\left[ u(\mu +\rho )-\rho \right] -%
\mathcal{D}_{\af_{\perp }}}}{\prod_{\beta \in \Delta _{\af_{\perp
}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af%
_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] }.
\end{eqnarray*}
\end{proof}

\begin{remark}
This relation can be considered a generalized form of the Weyl formula for singular
element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\af}\left(
u\right) $ play the role of singular weights while instead of the determinants $%
\epsilon (u)$ we have the products $\epsilon (u)\mathrm{\dim }\left( L_{%
\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left(
u\right) }\right) .$ In fact when $\frak{a=g}$ both $\af_{\perp }$ and $%
\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
easily reobtained.
\end{remark}

\subsubsection{Constructing recurrent relations.}
\label{subsec:Construct-recurrent-rel}

Consider the right-hand side of relation (\ref{eq:4}).
The numerator there describes the branching in terms of singular elements and
it is reasonable to expand it as an element of $\mathcal{E}\left( \frak{g} \right)$:
\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }.
\end{equation}
Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signs
depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
$k_{\lambda}^{\left( \mu \right) }$'s is that they coincide with the branching coefficients
for all weights $\nu$ inside the main Weil chamber:
\begin{equation}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}.
\label{eq:21-1}
\end{equation}
We call the coefficients $k_{\lambda}$ --- the anomalous branching coefficients
(see also \cite{ilyin812pbc}).

Now we can state the main theorem which gives us an instrument for the
recurrent computation of branching coefficients.

\begin{theorem}
  For the anomalous branching coefficients $k^{(\mu)}_{\nu}$ (\ref{eq:21})
  the following relation holds
  \begin{equation}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{u\in U} \epsilon(u)\;
        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
\end{theorem}
\begin{proof}
Redress relation (\ref{eq:4}) for the element $
\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
for the carrier $\Phi _{\af\subset \frak{g}}$ ,
\begin{equation*}
\begin{array}{l}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
\right) = \\[2mm]
=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left(
1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
+\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right)  \\
=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right) .
\end{array}
\end{equation*}

Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
):
\begin{equation*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
\af_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{eqnarray*}
The immediate consequence of this equality is:
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\af}.  \label{eq:17}
\end{equation}
The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
are subject to linear relations and the form of these relations changes
when the tested weight $\xi $ coincides with one of \ the ''singular
weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
}\subset \frak{g}}$ and pass to a summation over the vectors of the
injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see Definition \ref
{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
\end{proof}

\subsubsection{Embeddings and orthogonal pairs in simple Lie algebras}
\label{sect-embeddings}
